\textbf{Political Instability and Financial Markets}

### 2017-08-20 doc/paper.tex
Minor changes to prose and figure placement in Section 3, and changes to visualization of Figure 2

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of Coup d'Etat}
\label{tab:coup list}\\
\vspace{-5pt}\\
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\endfirsthead
\multicolumn{3}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\hline
\endhead
\hline 
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
06/08/1970 & Argentina & Authoritarian to authoritarian\\
03/22/1971 & Argentina & Authoritarian to authoritarian\\
03/24/1976 & Argentina & Democratic to authoritarian\\
10/06/1976 & Thailand & Democratic to authoritarian\\
10/20/1977 & Thailand & Authoritarian to authoritarian\\
12/12/1979 & South Korea & Authoritarian to authoritarian\\
02/23/1991 & Thailand & Democratic to authoritarian\\
04/05/1992 & Peru & Democratic to authoritarian\\
10/12/1999 & Pakistan & Democratic to authoritarian\\
10/04/2002 & Nepal & Democratic to authoritarian\\
09/19/2006 & Thailand & Democratic to authoritarian\\
01/11/2007 & Bangladesh & Authoritarian to authoritarian\\
04/11/2002 & Venezuela & Failed authoritarian to democratic\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize

@@

We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns. \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}. \footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}

@@

The average coup has a $-2.5\%$ event day AR. Event day ARs for the 1970 coup in Argentina, the 1979 coup in South Korea, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero. Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero. In all of these cases, the coup in question either overthrew a democratically elected government or changed governance from one military ruler to another. The initial negative reaction followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.

Event day ARs are negative for all coups except the 1971 coup in Argentina and the 2002 failed coup d'etat attempt against Hugo Chavez. These results provide evidence that that coups can in fact result in positive abnormal returns. While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies. The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.

>>>>

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of Coup d'Etat}
\label{tab:coup list}\\
\vspace{-5pt}\\
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\endfirsthead
\multicolumn{3}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\hline
\endhead
\hline 
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
06/08/1970 & Argentina & Authoritarian to authoritarian\\
03/22/1971 & Argentina & Authoritarian to authoritarian\\
03/24/1976 & Argentina & Democratic to authoritarian\\
10/06/1976 & Thailand & Democratic to authoritarian\\
10/20/1977 & Thailand & Authoritarian to authoritarian\\
12/12/1979 & South Korea & Authoritarian to authoritarian\\
02/23/1991 & Thailand & Democratic to authoritarian\\
04/05/1992 & Peru & Democratic to authoritarian\\
10/12/1999 & Pakistan & Democratic to authoritarian\\
10/04/2002 & Nepal & Democratic to authoritarian\\
09/19/2006 & Thailand & Democratic to authoritarian\\
01/11/2007 & Bangladesh & Authoritarian to authoritarian\\
04/11/2002 & Venezuela & Partial/failed authoritarian to democratic\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize

@@

We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns. \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat. Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).} \autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the partial/failed Venezuelan coup attempt of 2002. We examine this event as well, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.

@@

The average coup has a $-2.5\%$ event day AR. Event day ARs for the 1970 coup in Argentina, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero. Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero. In all of these cases, the coup in question either overthrew a democratically elected government or changed governance from one military ruler to another. The initial negative reaction followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.

Event day ARs are negative for all coups except the 1971 coup in Argentina and the 2002 failed coup d'etat attempt against Hugo Chavez (\autoref{fig:AR-Ven}). These results provide evidence that coups can in fact result in positive abnormal returns. While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies. The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
